---
title: "Untitled"
author: "Shanu Agrawal"
date: "5/3/2019"
output: html_document
---
Problem 
In order for an insurance company to make money, it needs to collect more in yearly
premiums than it spends on medical care to its beneficiaries. As a result, insurers
invest a great deal of time and money to develop models that accurately forecast
medical expenses.

The insurance.csv file includes 1,338 examples of beneficiaries currently enrolled
in the insurance plan, with features indicating characteristics of the patient as well as
the total medical expenses charged to the plan for the calendar year. The features are:
• age: This is an integer indicating the age of the primary beneficiary (excluding
those above 64 years, since they are generally covered by the government).
• sex: This is the policy holder's gender, either male or female.
• bmi: This is the body mass index (BMI), which provides a sense of how over
or under-weight a person is relative to their height. BMI is equal to weight (in
kilograms) divided by height (in meters) squared. An ideal BMI is within the
range of 18.5 to 24.9.
• children: This is an integer indicating the number of children / dependents
covered by the insurance plan.
• smoker: This is yes or no depending on whether the insured regularly
smokes tobacco.
• region: This is the beneficiary's place of residence in the U.S., divided into
four geographic regions: northeast, southeast, southwest, or northwest.

Step 1: exploring and preparing the data
```{r setup, include=FALSE}
#predicting medical expenses using linear regression
insurance_data<- read.csv("D:/work/Shanu/ATI/Base_Analytics/class4/insurance.csv", stringsAsFactors = FALSE)

#Check the Structure of data
str(insurance_data)

#Check the summary of data, if any missing values NA 
summary(insurance_data)

#Check first few rows
head(insurance_data)

library(esquisse)
esquisse::esquisser()

```


```{r}

```



```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}

```

